The Skew-Normal Approximation of the Binomial Distribution

### 2011-01-20 project/paper/intro.tex
Added normal pdf to intro footnote.

where $q=1-p$. Calculating the binomial cumulative distribution function (cdf),
$F_X(x) = P(X \leq x) = \sum_{k=1}^x f_X(k)$, by hand is manageable for small
$n$ but quickly becomes cumbersome as $n$ grows even moderately large. A common
strategy is to use the normal distribution as an approximation:

@@

where $\Phi$ is the standard normal\footnote{Let $X \sim Z = N(0, 1)$. Then $X$
is said to be a standard normal distribution with pdf

and cdf given by $\Phi(z) = \int_{-\infty}^z \phi(t) \; dt$. Equations 3.3.29
and 3.3.30, \citet{textbook}.} cdf and $\mu = np$ and $\sigma =
\sqrt{np(1-p)}$.

>>>>

where $q=1-p$. Calculating the binomial cumulative distribution function (cdf),
$F_X(x) = P(X \leq x) = \sum_{k=1}^x f_X(k)$, by hand is manageable for small
$n$ but quickly becomes cumbersome as $n$ grows even moderately large. A common
strategy is to use the normal distribution\footnote{A random variable $X$
follows the normal distribution with mean $\mu$ and variance $\sigma^2$ if it
has the pdf

\begin{equation*}
  f(x;\mu,\sigma) = \frac{1}{\sqrt{2\pi}\,\sigma} \; e^{-[(x-\mu)/\sigma]^2/2}
\end{equation*}

for $-\infty < x < \infty$, where $-\infty < \mu < \infty$ and $0 < \sigma <
\infty$. This is denoted by $X \sim N(\mu,\sigma^2)$.\\

$N(0,1)$ is an important special case known as the standard normal (denoted
$Z$) and has pdf

and cdf given by $\Phi(z) = \int_{-\infty}^z \phi(t)\;dt$.\\

Equations 3.3.27, 3.3.29, and 3.3.30, \citet{textbook}.} as an approximation:

@@

where $\Phi$ is the standard normal cdf and $\mu = np$ and $\sigma =
\sqrt{np(1-p)}$.
